### 2016-02-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added to FDS input file and to exp. description report

@@

>>>>

% Load Packages
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{lscape}

@@

\section{East Structure}
3 sets of 3 sequences: Tests 2-4; Test 5; Test 6

Burners on $\rightarrow$ Ventilation changed by opening/closing doors or roof vent $\rightarrow$ Burners off

\begin{landscape}
\begin{table}[!ht]
\caption{East Structure experimental event times (mm:ss)}
\begin{tabular}{lcccccccccccccc}
 \toprule
% \begin{tabular}{@{}l@{}} \textbf{Test} \\ \textbf{Number} \end{tabular} & 
% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Corner} \\ \textbf{Burner} \end{tabular}} & 
% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Middle} \\ \textbf{Burner} \end{tabular}} & 
% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Center} \\ \textbf{Burner} \end{tabular}} & 
% \begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{West Double Door} \end{tabular} & 
% \begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{East Double Door} \end{tabular} &
% \begin{tabular}{@{}c@{}} \textbf{South Side} \\ \textbf{Single Door} \end{tabular} &
% \begin{tabular}{@{}c@{}} \textbf{Roof Vent} \\ \textbf{Single Door} \end{tabular}
\textbf{Test} & 
\multicolumn{2}{c}{\textbf{\underline{Corner Burner}}} & 
\multicolumn{2}{c}{\textbf{\underline{Middle Burner}}} & 
\multicolumn{2}{c}{\textbf{\underline{Center Burner}}} & 
\multicolumn{2}{c}{\textbf{\underline{W Double Door}}} & 
\multicolumn{2}{c}{\textbf{\underline{E Double Door}}} & 
\multicolumn{2}{c}{\textbf{\underline{Single Door}}} & 
\multicolumn{2}{c}{\textbf{\underline{Roof Vent}}}
\\
\textbf{Number} & 
\textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & 
\textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open} &
\textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open}
\\
\midrule
% Test 2
2 & 0:20 & 16:20 & 3:20 & 14:20 & 6:20 & 12:20 & 
N/A & 7:20 & N/A & 9:20 & N/A & 10:30 & N/A & N/A \\
% Test 3
3 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A \\
% Test 4
4 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A 
\\ \multicolumn{15}{c}{ } \\
% Test 5a
5a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
N/A & 3:18 & N/A & 6:18 & N/A & N/A & 7:45 & 2:53 \\
% Test 5b
5b & 0:15 & 10:30 & 0:30 & 10:15 & 0:45 & 10:00 & 
N/A & 3:45 & N/A & 5:15 & N/A & N/A & 8:30 & 2:15 \\
% Test 5c
5c & 0:15 & 9:45 & 0:30 & 9:30 & 0:45 & 9:15 & 
N/A & 3:45 & N/A & 5:16 & N/A & N/A & 7:28 & 2:15
\\ \multicolumn{15}{c}{ } \\
% Test 6a
6a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
% Test 6b
6b & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
% Test 6c
6c & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
\bottomrule
\end{tabular}
\label{table:east_exp_times}
\end{table}
\end{landscape}
